---
title: "Coding challange 4"
author: "Prasanna"
date: "2026-02-19"
output:
  html_document:
    toc: true
    toc_float: true
---
- Noel, Z.A., Roze, L.V., Breunig, M., Trail, F. 2022. Endophytic fungi as
promising biocontrol agent to protect wheat from Fusarium graminearum
head blight. Plant Disease. [DOI](https://doi.org/10.1094/PDIS-06-21-1253-RE)


### 1. 
- a. 
- b.

### 2
```{r warning=FALSE, echo=FALSE}

library(tidyverse)
library(ggpubr)
library(ggrepel)
```

```{r warning=FALSE, echo=FALSE}
MycotoxinData=read.csv ("MycotoxinData.csv", na.strings = "na") #file path to GitHub repository
```
- I.Using ggplot, create a boxplot of DON by Treatment 
- II. Change the factor order level so that the treatment “NTC” is first, followed by “Fg”, “Fg + 37”, “Fg + 40”, and “Fg + 70.

```{r echo=FALSE, warning=FALSE}
MycotoxinData$Cultivar <- as.factor(MycotoxinData$Cultivar)
    MycotoxinData$Treatment <- factor(MycotoxinData$Treatment,levels = c("NTC", "Fg", "Fg + 37", "Fg + 40", "Fg + 70"))
    Fig1 <- ggplot(MycotoxinData, aes(x = Treatment, y = DON, fill = Cultivar)) +
        geom_boxplot(position = position_dodge()) +
        geom_point(position = position_jitterdodge(), alpha = 0.6) +
        scale_fill_manual(values = c("orange", "blue")) +
        xlab("") +
        ylab("DON (ppm)") +
        facet_wrap(~ Cultivar) +
        theme_classic()
    print(Fig1)
```

- III. Change the y-variable to plot X15ADON and MassperSeed_mg. 

```{r echo=FALSE, warning=FALSE}
 MycotoxinData$Cultivar <- as.factor(MycotoxinData$Cultivar)
      MycotoxinData$Treatment <- factor(MycotoxinData$Treatment,levels = c("NTC", "Fg", "Fg + 37", "Fg + 40", "Fg + 70"))
      Fig2 <-   ggplot(MycotoxinData, aes(x = Treatment, y = X15ADON, fill = Cultivar)) +
            geom_boxplot(position = position_dodge()) +
            geom_point(position = position_jitterdodge(), alpha = 0.6) +
            scale_fill_manual(values = c("orange", "blue")) +
            xlab("") +
            ylab("X15ADON") +
            facet_wrap(~ Cultivar) +
            theme_classic()
      print(Fig2)
```

```{r echo=FALSE, warning=FALSE}
MycotoxinData$Cultivar <- as.factor(MycotoxinData$Cultivar)
    MycotoxinData$Treatment <- factor(MycotoxinData$Treatment,levels = c("NTC", "Fg", "Fg + 37", "Fg + 40", "Fg + 70"))
    Fig3 <-   ggplot(MycotoxinData, aes(x = Treatment, y = MassperSeed_mg, fill = Cultivar)) +
          geom_boxplot(position = position_dodge()) +
          geom_point(position = position_jitterdodge(), alpha = 0.6) +
          scale_fill_manual(values = c("orange", "blue")) +
          xlab("") +
          ylab("MassperSeed_mg") +
          facet_wrap(~ Cultivar) +
          theme_classic()
    print(Fig3)
```
- IV. Use ggarrange function to combine all three figures into one with three columns and
one row. Set the labels for the subplots as A, B and C. Set the option common.legend = T
within ggarage function

```{r echo=FALSE, warning=FALSE}
figure_combined <- ggarrange(
  Fig1,
  Fig2,
  Fig3,
  labels = "auto",  
  nrow = 1,
  ncol = 3,
  common.legend = TRUE,  
  legend = "top")
print(figure_combined)
```
- V.Use geom_pwc() to add t.test pairwise comparisons to the three plots made above.
```{r echo=FALSE, warning=FALSE}
Fig1a <- Fig1 + 
geom_pwc(aes(group = Treatment), method = "t_test", label = "p.adj.format")        
print(Fig1a)

Fig2a <- Fig2 + 
  geom_pwc(aes(group = Treatment), method = "t_test", label = "p.adj.format")     
print(Fig2a)

Fig3a <- Fig3 + 
  geom_pwc(aes(group = Treatment), method = "t_test", label = "p.adj.format")     
print(Fig3a)

### Integration of pairwise comparison results into a single plot  ###
figure_combined_final <- ggarrange(
  Fig1a,
  Fig2a,
  Fig3a,
  labels = "auto",  
  nrow = 1,
  ncol = 3,
  common.legend = TRUE,  
  legend = "top")
print(figure_combined_final)
```

