
---
title: "Bonus Material"
author: "Prasanna"
output:
  html_document:
    variant: gfm
---

# 1. Give me notes on the recap material. These questions focus on material that students commonly struggle

## data subsetting

### Used the mtcars as example dataset
```{r}
mtcars
```

## without subset function

### Give the name of the data set then open square bracket[raw,]column
```{r}
mtcars [1,] # raw one only
mtcars [1,3] # raw one column 3
```

### find all rows such tha vs=1 data frame $ sign vs == 1 and need to put a comma

```{r}
mtcars [mtcars$vs == 1,]
mtcars $hp[mtcars$vs == 1] # no comma allows to access all row and column
mtcars $hp[mtcars$vs == 1][1] # get the first number there
mtcars $hp[mtcars$vs == 1 & mtcars$gear == 4] # and function
max (mtcars$hp) # get the maximum value of the mtcars hp row
```

### Subset with subset function
```{r}
subset(mtcars, vs==1)
subset(mtcars, vs==1 & gear == 4) # and
subset(mtcars, vs==1 | gear == 4) # or

```
# 2. Complete one of the extra optional materials provided, or explore a topic of your choice, or find a topic online and explore the code and how it works.

### Write a short justification (2–3 sentences): Why did you choose this? What did you want to learn?


# 3. Introduction to renv. 

## Follow the coding demonstration in class. Turn in notes

### renv package

- Packages are installed globally so versions may differ between machines
- This causes code to break when you move project and not reproducible
- renv is used to make a project specific library taht ensure the reproducibility and portability across different computers

### Make a GitHub repository first. For this I used the already created class 

### Next, load necessary packages need to work 

```{r}
library(ggplot2)
 library(dplyr)
```
### creat an renv libry and lock file on my computer


- Run code in console as renv:init
- Run code in console as renv::snapshot() 
- These codes create a project specific library that contain all packages and rnew.lock files that contain the versions of all packages.
- Commit and push these files into GitHub

### Run the renv in a differet computer

- Download the repository file on GitHub that should have the codes used for the first project as well
- Run code in console renv::restore()
- The new computer is ready to open the packages library with similar version as did in first work to ensure the reproducibility. 
_ We can run the codes







